Consumption and resistance across states and HRRs

### 2017-03-14 states/resistance/state-report.Rmd
many changes
added theil-sen

@@

>>>>

# To do

- Implement weights in the linear correlations
- Join multiple results into one table, or do pairwise comparisons of analytical methods

@@

#### State-level resistance-averaged robust regressions

```{r}
library(mblm)

safe_mblm = function(data, indep, expl) {
  try(return(mblm(sprintf('%s ~ %s', indep, expl), data) %>% tidy), silent=TRUE)
  data_frame(term=expl, estimate=NA, std.error=NA, statistic=NA, p.value=1.0)
}

ts_models = function(df, indep) {
  lapply(c('cpkp', 'did'), function(expl) {
    safe_mblm(df, indep, expl) %>%
      filter(term==expl) %>%
      rename(explanatory=term) %>%
      verify(nrow(.) == 1)
  }) %>% bind_rows
}

ts_models_result = function(x, this_place) {
  x %>%
    group_by_('bug', 'drug_group', this_place) %>%
    summarize(mean_nonsus=mean(percent_nonsusceptible, na.rm=TRUE),
              cpkp=head(cpkp, 1),
              did=head(did, 1)) %>%
    group_by(bug, drug_group) %>%
    do(linear_models(., 'mean_nonsus')) %>%
    ungroup %>%
    filter(!is.na(estimate)) %>%
    mutate(adj.p.value=p.adjust(p.value, method='BH'),
           sig=pvalue_stars(adj.p.value)) %>%
    select(bug, drug_group,
           explanatory, slope=estimate, p.value,
           adj.p.value, sig)
}

ts_state_res = linear_models_result(state_dat, 'state')

ts_state_res %>% kable
```
